Model-based variable selection for regression with highly correlated variables.

### 2014-08-22 www/article.tex
up figure13
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@816 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@817 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

We define a {\it global} neighbourhood space $\mathcal{V}(\boldsymbol{S})$ of $\boldsymbol{S}$ composed by the following four {\it specific} neighbourhood spaces $\mathcal{V}(\boldsymbol{S})=\mathcal{V}_{r+}(\boldsymbol{S})\cup\mathcal{V}_{r-}(\boldsymbol{S})\cup\mathcal{V}_{p+}(\boldsymbol{S})\cup\mathcal{V}_{p-}(\boldsymbol{S})$ described below:
	\begin{itemize}
	\item {\bf Adding a sub-regression}: a new sub-regression with only one predictor covariate is added to $\boldsymbol{S}$
\begin{equation}
\mathcal{V}_{r+}(\boldsymbol{S}) = \left\{\tilde{\boldsymbol{S}}: \tilde{\boldsymbol{S}}\in\mathcal{S}, (\tilde{\boldsymbol{J}_r},\tilde{\boldsymbol{J}_p})^{1,\ldots,d_r}=(\boldsymbol{J}_r,\boldsymbol{J}_p), \tilde{J}_r^{d_r+1}\in J_f, \tilde{J}_p^{d_r+1}=\{j\}, j\in J_f \right\}.
\end{equation}	
		\item {\bf Removing a sub-regression}: a sub-regression with only one predictor covariate is removed from $\boldsymbol{S}$
\begin{equation}
\mathcal{V}_{r-}(\boldsymbol{S}) = \left\{\tilde{\boldsymbol{S}}: \tilde{\boldsymbol{S}}\in\mathcal{S}, (\tilde{\boldsymbol{J}_r},\tilde{\boldsymbol{J}_p})=(\boldsymbol{J}_r,\boldsymbol{J}_p)^{\{1,\ldots,d_r\}\backslash j}, j\in\{1,\ldots,d_r\} \right\}.
\end{equation}	
	\item {\bf Adding a predictor covariate}: a predictor covariate is added to one sub-regression of $\boldsymbol{S}$
\begin{equation}
\mathcal{V}_{p+}(\boldsymbol{S}) = \left\{\tilde{\boldsymbol{S}}: \tilde{\boldsymbol{S}}\in\mathcal{S}, \tilde{\boldsymbol{J}_r}=\boldsymbol{J}_r, \tilde{J}_p^{j}=\tilde{J}_p^{j} \cup \{h\}, j\in \{1,\ldots,d_r\}, h\in J_f \right\}.
\end{equation}
	\item {\bf Removing a predictor covariate}: a predictor covariate is removed from one sub-regression of $\boldsymbol{S}$
\begin{equation}
\mathcal{V}_{p-}(\boldsymbol{S}) = \left\{\tilde{\boldsymbol{S}}: \tilde{\boldsymbol{S}}\in\mathcal{S}, \tilde{\boldsymbol{J}_r}=\boldsymbol{J}_r, \tilde{J}_p^{j}=\tilde{J}_p^{j} \backslash \{h\}, j\in \{1,\ldots,d_r\}, h\in J_f \right\}.
\end{equation}	
	\end{itemize}

@@

\paragraph{Comparisons 2 to 4} We compare now three variable selections methods: {\sc lasso} with {\sc CorReg}+{\sc lasso}, elasticnet with {\sc CorReg}+electicnet and also stepwise with {\sc CorReg}+stepwise. Figures \ref{toutlar}, \ref{toutelast} and \ref{toutstepwise} respectively display the results on the same manner as the previous {\sc ols} with {\sc CorReg}+{\sc ols}. We see that {\sc CorReg}, used as a pre-treatment, provides similar prediction accuracy as the three variable selection methods (this prediction is often better for small datasets) but with much more parsimonious regression models on $\boldsymbol{Y}$. This is remarkable because the true model depends on all covariates, so it highlight that other variable selection methods may be really penalized by the correlations between the covariates.

@@

 \begin{figure}[h!] 
	\begin{minipage}[l]{.48\linewidth}
			\includegraphics[height=180px,width=245px]{figures/res_article/robust_S.png} 
			\caption{Evolution of the quality of $\hat{\boldsymbol{S}}$ when the paramater $a$ increases.}\label{resnonlin}
	\end{minipage} \
   \begin{minipage}[r]{.48\linewidth}
			\includegraphics[height=180px,width=240px]{figures/res_article/robust_MSE.png} 
			\caption{{\sc mse} on the main regression for {\sc ols} (thick) and {\sc lasso} (thin) used both with (plain) or without {\sc CorReg} (dotted).}\label{MSEnonlin}
   \end{minipage}
\end{figure}

>>>>

We define a {\it global} neighbourhood space $\mathcal{V}(\boldsymbol{S})$ of $\boldsymbol{S}$ composed by the following four {\it specific} neighbourhood spaces $\mathcal{V}(\boldsymbol{S})=\mathcal{V}_{r+}(\boldsymbol{S})\cup\mathcal{V}_{r-}(\boldsymbol{S})\cup\mathcal{V}_{p+}(\boldsymbol{S})\cup\mathcal{V}_{p-}(\boldsymbol{S})$ described below:
	\begin{itemize}
	\item {\bf Adding a sub-regression}: a new sub-regression with only one predictor covariate is added to $\boldsymbol{S}$
\begin{equation}
\mathcal{V}_{r+}(\boldsymbol{S}) = \left\{\tilde{\boldsymbol{S}}: \tilde{\boldsymbol{S}}\in\mathcal{S}, (\tilde{\boldsymbol{J}_r},\tilde{\boldsymbol{J}_p})^{1,\ldots,d_r}=(\boldsymbol{J}_r,\boldsymbol{J}_p), \tilde{J}_r^{d_r+1}\in J_f, \tilde{J}_p^{d_r+1}=\{j\}, j\in J_f \right\}.
\end{equation}	
		\item {\bf Removing a sub-regression}: a sub-regression  is removed from $\boldsymbol{S}$
\begin{equation}
\mathcal{V}_{r-}(\boldsymbol{S}) = \left\{\tilde{\boldsymbol{S}}: \tilde{\boldsymbol{S}}\in\mathcal{S}, (\tilde{\boldsymbol{J}_r},\tilde{\boldsymbol{J}_p})=(\boldsymbol{J}_r,\boldsymbol{J}_p)^{\{1,\ldots,d_r\}\backslash j}, j\in\{1,\ldots,d_r\} \right\}.
\end{equation}	
	\item {\bf Adding a predictor covariate}: a predictor covariate is added to one sub-regression of $\boldsymbol{S}$
\begin{equation}
\mathcal{V}_{p+}(\boldsymbol{S}) = \left\{\tilde{\boldsymbol{S}}: \tilde{\boldsymbol{S}}\in\mathcal{S}, \tilde{\boldsymbol{J}_r}=\boldsymbol{J}_r, \tilde{J}_p^{j}=\tilde{J}_p^{j} \cup \{h\}, j\in \{1,\ldots,d_r\}, h\in J_f \right\}.
\end{equation}
	\item {\bf Removing a predictor covariate}: a predictor covariate is removed from one sub-regression of $\boldsymbol{S}$
\begin{equation}
\mathcal{V}_{p-}(\boldsymbol{S}) = \left\{\tilde{\boldsymbol{S}}: \tilde{\boldsymbol{S}}\in\mathcal{S}, \tilde{\boldsymbol{J}_r}=\boldsymbol{J}_r, \tilde{J}_p^{j}=\tilde{J}_p^{j} \backslash \{h\}, j\in \{1,\ldots,d_r\}, h\in J_f \right\}.
\end{equation}	
	\end{itemize}

@@

\paragraph{Comparisons 2 to 4} We compare now three variable selections methods: {\sc lasso} with {\sc CorReg}+{\sc lasso}, elasticnet with {\sc CorReg}+electicnet and also stepwise with {\sc CorReg}+stepwise. Figures \ref{toutlar}, \ref{toutelast} and \ref{toutstepwise} respectively display the results on the same manner as the previous {\sc ols} with {\sc CorReg}+{\sc ols}. We see that {\sc CorReg}, used as a pre-treatment, provides similar prediction accuracy as the three variable selection methods (this prediction is often better for small datasets) but with much more parsimonious regression models on $\boldsymbol{Y}$. This is remarkable because the true model depends on all covariates, so it highlights that other variable selection methods may be really penalized by the correlations between the covariates.

@@

 \begin{figure}[h!] 
	\begin{minipage}[l]{.48\linewidth}
			\includegraphics[height=180px,width=245px]{figures/res_article/robust_S_art.png} 
			\caption{Evolution of the quality of $\hat{\boldsymbol{S}}$ when the paramater $a$ increases.}\label{resnonlin}
	\end{minipage} \
   \begin{minipage}[r]{.48\linewidth}
			\includegraphics[height=180px,width=240px]{figures/res_article/robust_MSE.png} 
			\caption{{\sc mse} on the main regression for {\sc ols} (thick) and {\sc lasso} (thin) used both with (plain) or without {\sc CorReg} (dotted).}\label{MSEnonlin}
   \end{minipage}
\end{figure}
